Do Non-Cognitive Skills Affect Employment Outcomes of Youth During the School-to-Work Transition?

### 2024-06-18 02_codes/paper_draft.qmd
text and folder structure

@@

Research questions

1\) do non-cognitive skills affect the probability of employment for youth during school-to-work transition? If yes, what are the most influential skills?

2\) does this effect is heterogeneous with respect to socio-economic status? in other words, which non-cognitive skills are the most important when it comes to the youth from the poorest households

@@

@@

## Econometric Verification Strategy

@@

### Non-Cognitive Skills of Youth

@@

### Socio-Demographic Profile of Employed Youth - ???

@@

We need to have two mlm models

1\)

@@

@@

@@

@@

>>>>

*Masych, Dikaya, Avanesian*

@@

Нужно дать обзор литературы, в которой некогнитивные навыки и личностные характеристики влияют на трудоустройство, особенно с прицелом на молодежь

Самая ранняя статья Рожковой (Вопросы Экономики) про отдачу от неекогнитивных навыков содержит блок про трудоустройство

То же самое касается препринта Гимпельсона, Зудиной и Капелюшникова.

Это все примеры про Россию.

Мы также можем сдкелать ссылки на статью Зудиной по НИТ, и нашу статью.

Но примеры нельзя ограничивать Россией и нужна хорошая международная литература - частично она уже упомянута в нашей статье.

Где-то во введении нужно также дать контекст и посмотреть данные Росстата по молодежной безработице в России, где из регионов она самая низкая и где самая высокая. Если молодежной безработицы нет, то можно просто безработицу. Несколько потенциальных источников

<https://cyberleninka.ru/article/n/molodezhnaya-bezrabotitsa-v-rossii-prichiny-i-puti-snizheniya/viewer>

<https://vital.lib.tsu.ru/vital/access/services/Download/vtls:000587153/SOURCE1>

Не нужно много о безработице, но необходимо дать контекст

Current study explores the impact of non-cognitive skills on employment outcomes of youth aged 15-29 during school-to-work transition in Russia. Based on data of Russia Longitudinal Monitoring Survey (RLMS), it aims to address the following research question: do non-cognitive skills affect the probability of employment for youth during school-to-work transition? If yes, what are the most influential skills? The consideration of this research question is guided by supplementary questions. First of all, the study aims to explore if the effect of non-cognitive skills on employment outcones is heterogeneous with respect to socio-economic status of an individual. in other words, which non-cognitive skills are the most important when it comes to the youth from the poorest households

-   calculate random slope terms for different completed education levels (make a separate regression model for each education level)

@@

*Egorova*

RLMS data for 2019 is to be used. Sample 15-29 years old as it aligns with ILO definition for school-to-work transition.

@@

## Methodology

*Avanesian*

@@

### Non-Cognitive Skills of Youth (NCS)

*Egorova*

@@

@@

*Avanesian*

We need to have three regression models

@@

*Masych, Dikaya*

@@

*Avanesian*

@@

*Masych*

@@

*Avanesian*

## References
